---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ZillowR

The ZillowR package provides an R interface to the Zillow Web Services API.

## Installation and setup

Install the latest stable version from CRAN as follows.

```{r, eval = FALSE}
install.packages('ZillowR')
```

Alternatively, if you've installed the devtools package, you can install the
latest development version directly from Github.

```{r, eval = FALSE}
devtools::install_github('fascinatingfingers/ZillowR')
```

Each subscriber to Zillow Web Services is uniquely identified by an ID
sequence, and every request to Web Services requires this ID. After loading the
ZillowR package, you should set the "ZillowR-zws_id" option as shown below. This
facilitates API calls without needing to specify your Zillow Web Services ID
every time.

```{r}
library(ZillowR)
set_zillow_web_service_id('YOUR ZWS-ID')
```

Click [here](http://www.zillow.com/webservice/Registration.htm) to register with
Zillow and receive your own Web Services ID.

## Basic usage

ZillowR provides an eponymous function for each Zillow API service, with API
parameters as function arguments. For example:

```{r, eval = FALSE}
GetMonthlyPayments(price = 300000L)
```

```{r, echo = FALSE}
testthat::with_mock(
    getURL = function(...) {
        readLines(
            system.file('xml_response_examples', 'GetMonthlyPayments.xml', package = 'ZillowR')
        )
    },
    GetMonthlyPayments(price = 300000L),
    .env = 'RCurl'
)
```

Each function returns a named list with the following elements:

  * **request:** a list with the request parameters
  * **message:** a list of status code(s) and message(s) returned by the API
  * **response:** an XMLNode with the API-specific response values. At this time,
    no further coercion is performed, so you may have to use functions from the
    `XML` package to extract the desired output.

Be sure to check out the [API documentation](http://www.zillow.com/howto/api/APIOverview.htm)
to learn more about the available services
